%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Sr. Full Stack Developer} % Job title
    {Sports IQ} % Organization
    {Remote} % Location
    {Aug. 2021 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed a bet settlement tool from scratch and deployed it with Firebase. (React, Redux, Okta, ExpressJS, BigQuery, Firebase)}
        \item {Took over ownership of a legacy odds adjustment console. Solved a memory leak that caused frequent crashes.}
        \item {Prioritized technical debt and new features for the trading console. Undertook massive Refactor.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer II} % Job title
    {Think Research Corp} % Organization
    {Toronto, ON} % Location
    {Oct. 2019 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on an Agile/Scrum team of 5 to develop features for a clinical note taking application.}
        \item {Overhauled our database models to allow for fast and lightweight auto-saves with conflict detection. Saw 80\% reduction in API response time after stress testing with Gatling.}
        \item {Architected and implemented an auto-save system that touched every layer of the stack. (React/Redux/Mobx, Rails/Redis/ActionCable/Active Record, PostgreSQL)}
        \item {Developed a concurrent editing system that allows clinicians to collaborate in real time without posing a risk to patient data. This feature allowed us to keep a client with a concurrent workflow.}
        %\item {Worked closely with the UX/UI team to provide effort estimates and pay off design debt. (React/Styled Components/CSS)}
        %\item {Developed a debug tool for viewing the HTML which is generated by our form JSON to PDF service.}
        \item {Migrated our application's Helm charts to a much simpler Kustomize manifest.}
        \item {Gave technical presentations to the Engineering department at the end of each sprint (In-person and remotely).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Test Engineer} % Job title
    {Celestica Inc} % Organization
    {Toronto, ON} % Location
    {May. 2016 - Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed automated testing solutions for consumer electronics in a factory refurbishment setting. (Python/LabVIEW)}
        %\item {Developed a versatile barcode scanning tool that allowed any style of barcode (including 2D with multiple fields) to be scanned and parsed using regex. Simple configuration via JSON file.}
        \item {Leveraged image processing techniques to write a quality assurance tool to process images of LEDs. Identified multiple LEDs in a single image and evaluated them for colour and brightness. (Python/OpenCV)}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
